%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage[francais]{babel}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Yanxin}
\familyname{GONG}
\title{Résumé}
\address{32 Rue Eugene Jacquet}{60200 COMPIEGNE}    % optional, remove the line if not wanted
\mobile{+33 06 30 02 14 80}                    % optional, remove the line if not wanted
\email{yanxin.gong22@gmail.com}                      % optional, remove the line if not wanted
\homepage{http://www.yanxin.me}                % optional, remove the line if not wanted
\extrainfo{Come from: China} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2011--2014}{IT network system}{\small UTC Université Technologie de Compiègne}{}{}{}
% \cvline{advisor:}{\small Professor Mutlu Ozdogan}
% \cvline{advisor:}{\small Professor Eric Bach}
\cventry{2009--2011}{Engineering preparatory course}{\small ESIGELEC}{}{}{}
% \cvline{gpa:}{\small 3.76/4.0}
% \cvline{honors:}{\small Cum Laude}


\section{Professional Experience}

\cventry{2013}{Real time data analyze project}{UTC}{NodeJS}{6 months}
{
- This project is about some qualitative tests of the sunlight radiation data.\newline 
- First of all, the designed program allows to fetch data from data logger or monitor some data files. And then, it will generate a data stream and test this stream with some physic formulas. The errors of data can trigger the mail system to send a warning email.\newline
- This whole project has been developed in NodeJS.
}

\cventry{2012}{BIG DATA \& Cloud Computing intern}{Samber Valley}{NodeJS, MongoDB, websocket}{6 months}
{
- Coding of a statistic server with \textbf{MongoDB} query-language and designing of a \textbf{real time} publish-subscribe system.\newline
- Calculation \textbf{performance improved} : streaming, good choice of the index, splitted tables.\newline
- BIG DATA handled by MongoDB's \textbf{MapReduce}
}

\cventry{}{Database design project}{}{}{4 students 5 months}
{
- Conceptual \textbf{modeling} in UML and project management.\newline
- Website construction using PHP, Bootstrap and PostgreSQL.
}

\cventry{2010--2011}{Personal project}{mini game labyrinth}{C}{}
{Building and programming my own algorithm which allows a few paths.}

\section{IT}
\cvline{Languages}{C, NodeJS, JS, CSS/HTML, PHP, Java, shell, bash, scilab.}
\cvline{Database}{PostgreSQL, MongoDB, Oracle}
\cvline{Techinologies}{Bootstrap, Git, \LaTeX{}, memcache, MongoDB clusting/segmentation/dépoiement, CORBA, WebService, J2EE, Apache, Proxmox, OpenVZ}
\section{Speaking Skills}
\cvline{}
{
- Mandarin \& Cantonese, mother tongue.\newline
- English, do well in reading, writing and speaking.\newline
- French, fluent and accurate.
}

\section{Community}
\cvline{MongoDB}{DBA \href{http://education.10gen.com/downloads/certificates/b205d59b42754ead87e99667973d51ae/Certificate.pdf}{offical certificated}.}
\cvline{Github}{ID : \href{https://github.com/GGYaX}{GGYaX}.}

\end{document}
